---
title: "Lab 4 Solutions"
author: ""
date: ""
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

## Packages

```{r}
library(tidyverse)
```

## NC absentee voting data

>Voter information includes name, demographics, mailing address, precinct, and 
district data. Ballot information for voting by mail includes request date, 
send date, return date, return status (e.g., ACCEPTED, SPOILED, etc.), and 
mailing address(es). Ballot information for one-stop early voting includes 
voting date (called return date), early voting site, and same-day registration 
information. For full list of variables included, see 
[file layout](https://s3.amazonaws.com/dl.ncsbe.gov/ENRS/layout_absentee.txt).
<br/><br/>
*Source*: https://www.ncsbe.gov/results-data/absentee-data

```{r get_data}
base_url <- "https://s3.amazonaws.com/"
zip_url <-str_c(base_url, "dl.ncsbe.gov/ENRS/2020_11_03/absentee_20201103.zip")
download.file(url = zip_url, destfile = "absentee_votes.zip")
unzip("absentee_votes.zip")
absentee <- read_csv("absentee_20201103.csv")
```

## Visualizations

Create a bar plot of the number of ballot received by ballot send date.

See `images/visualizaiton_1.png`.

```{r}
absentee %>% 
  count(ballot_send_dt) %>% 
  ggplot(mapping = aes(x = ballot_send_dt, y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "Ballot send date", y = "Count") +
  theme_minimal()
```

Create a bar plot showing the number of ballots received on 09/04/2020 by 
county. Only show the top 20 counties as determined by number of
ballots received on 09/04/2020.

See `images/visualizaiton_2.png`.

```{r}
absentee %>% 
  filter(ballot_send_dt == "09/04/2020") %>% 
  count(county_desc) %>% 
  arrange(desc(n)) %>% 
  slice(1:20) %>% 
  ggplot(aes(x = reorder(county_desc, n), y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "County", y = "Count") +
  coord_flip() +
  theme_minimal()
```

Create a histogram based on the proportion of accepted ballots on a per
county basis.

See `images/visualizaiton_3.png`.

```{r}
absentee %>% 
  group_by(county_desc) %>% 
  count(ballot_rtn_status) %>% 
  mutate(proportion = n / sum(n)) %>% 
  ungroup() %>% 
  filter(ballot_rtn_status == "ACCEPTED") %>% 
  ggplot(aes(x = proportion)) +
  geom_histogram(binwidth = 0.02) +
  labs(x = "Proportion of ballots accepted", y = "Count") +
  theme_minimal(base_size = 16)
```

Create comparison box plots based on the age of absentee/mail-in voters
from the parties "DEM", "REP", "UNA" broken down by race.

See `images/visualizaiton_4.png`.

```{r}
absentee %>% 
  filter(voter_party_code %in% c("DEM", "REP", "UNA")) %>% 
  ggplot(aes(x = voter_party_code, y = age, fill = race)) +
  geom_boxplot() +
  scale_x_discrete(labels = c("Democrat", "Republican", "Unafilliated")) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  labs(x = "Voter party", y = "Age", fill = "")
```


